### 2015-08-18 LaTeX/Revision/editor.tex
baseline model disc, sep fixefvre from paper

\textcolor{blue}{\emph{stuff}}

@@

\textcolor{blue}{\emph{stuff}}

@@

\textcolor{blue}{\emph{stuff}}

@@

\textcolor{blue}{\emph{stuff}}

>>>>

\textcolor{blue}{\emph{
	For the ``Capital City'' and ``Any Major City'' models we ran a Hausman test to see if fixed or random effects were appropriate for our dataset, and in both cases we do not reject the null hypothesis of the Hausman test at a 90 or 95\% confidence interval indicating that it is acceptable to use random effects. We have added a discussion of this analysis into our empirical section.  
	However, as Clark \& Linzer (2015) show the Hausman test is by itself not a sufficient statistic to choose between fixed or random effects. They provide a typology for assessing whether or not to use fixed or random effects. Specifically they suggest to look at the ``the size of the dataset (both number of units and number of observations per unit), the level of correlation between the covariate and unit effects, and the extent of within-unit variation in the independent variable relative to the dependent variable'' (pg., 2). We employ their typology to further test whether our choice of random effects over fixed effects is appropriate. 
}}

@@

\textcolor{blue}{\emph{
	Including an interaction in this way is problematic for estimating the effect of conflict distance on conflict. The logged, minimum distance variable ranges from approximately 0.33 to 7.31, with closer values indicating that conflict is more proximate to an urban center for that country-conflict-year. This variable is NA for cases in which no conflict occurred for a given country year, thus before we interact it with the civil war variable in a full panel set up we would need to introduce some values for the NAs. One possibility is to simply invert the distance variable and then set the NAs to zero. However, the choice of introducing a zero for the NAs would be arbitrary and problematic, as our variable would no longer truly be continuous. Instead it would be discontinous in that we would have a large lump of observations at zero and then no observations until 1/7.31. Beyond the problems associated with transforming the variable in this way we would also run into issues of perfect collinearity with the inverted conflict distance measure and the interaction variable. The collinearity would result because the binary conflict variable is zero for every case that the inverted conflict distance variable is zero and one otherwise, meaning that multiplying the two will simply result in the inverted conflict distance variable again. 
	We have spent a fair bit of time trying to think of alternative approaches to modeling this in a full panel context using mixture or hierarchical approaches, but could find no mentions to develop a model for this type of data. 
	Despite this we strongly feel that our results are illustrative of an important and meaningful finding for the conflict literature. There has been very little discussion of the role that the spatial distribution of conflict plays in shaping macroeconomic outcomes, and the findings that we present here are the first to begin to disentangle this relationship.
}}

@@

\textcolor{blue}{\emph{
	stuff
}}

@@

\textcolor{blue}{\emph{
	We retested our hypothesis using the ACLED dataset and here as well we find that our distance measure of conflict to major urban centers is significantly negative. 
}}

### 2015-08-18 LaTeX/RhodiumEmp.tex
baseline model disc, sep fixefvre from paper

To estimate variation in growth rates, we use a random effects model clustered on countries. A random effects specification is preferred to using fixed effects here as we are not interested in estimating the change in GDP within units over time, rather our purpose is to explain variation between units. However, to ensure that it is also statistically justifiable to make this choice we run a Hausman specification test \citep{greene:2008}. For both the minimum conflict distance to any and to capital city specifications we fail to reject the null hypothesis at either the 90 and 95\% confidence intervals, providing at least some initial evidence that we are justified in our choice. However, as \citet{clark:linzer:2015} note not finding a significant difference through the Hausman test does not necessarily mean ``that the random effects is `safely` free from bias, and therefore to be preferred over the fixed effects estimator'' (pg., 2). We utilize their more nuanced typology for further arbitrating between fixed and random effects.

@@

\begin{align*}
	\% \Delta GDP_{i,t} &= \beta_{1}(Ln(Min. \; Conflict \; Dist.)_{i,t-1}) \\
	& \;+\; \beta_{2}(Conflict \; Intensity_{i,t-1}) \;+\; \beta_{3}(Conflict \; Duration_{i,t-1}) \\
	& \;+\; \beta_{4}(Conflict \; Area_{i,t-1} \;/\; Land \; Area_{i,t-1}) \\
	& \;+\; \beta_{5}(Number \; of \; Conflicts_{i,t-1}) \;+\; \beta_{6}(Upper \; Income_{i,t}) \\	
	& \;+\; \beta_{7}(Inflation_{i,t-1}) \;+\; \beta_{8}(Democracy_{i,t-1}) \\
	& \;+\; \beta_{9}(Resource \; Rents/GDP_{t-1}) \;+\; \beta_{10}(World \; GDP \; Growth_{t}) \\
	& \;+\; \mu_{i,t} \;+\; \epsilon_{i,t}
\end{align*}

@@

% Note to Ben: Anything you think we should say about the two surprising findings above

>>>>

To estimate variation in growth rates, we use a random effects model clustered on countries. A random effects specification is preferred to using fixed effects here as we are not interested in estimating the change in GDP within units over time, rather our purpose is to explain variation between units. However, to ensure that it is also statistically justifiable to make this choice we run a Hausman specification test \citep{greene:2008}. For both the minimum conflict distance to any and to capital city specifications we fail to reject the null hypothesis at either the 90 and 95\% confidence intervals, providing at least some initial evidence that we are justified in our choice. However, as \citet{clark:linzer:2015} note not finding a significant difference through the Hausman test does not necessarily mean ``that the random effects is `safely` free from bias, and therefore to be preferred over the fixed effects estimator'' (pg., 2). We utilize their more nuanced typology for further arbitrating between fixed and random effects, and again we find that random effects are preferred in this case.\footnote{A lengthier discussion of the \citet{clark:linzer:2015} procedure and its application to our data can be found in the Appendix.}

@@

\begin{align*}
	\% \Delta GDP_{i,t} &= \beta_{1}(Ln(Min. \; Conflict \; Dist.)_{i,t-1}) \\
	& \;+\; \beta_{2}(Conflict \; Intensity_{i,t-1}) \;+\; \beta_{3}(Conflict \; Duration_{i,t-1}) \\
	& \;+\; \beta_{4}(Conflict \; Area_{i,t-1} \;/\; Land \; Area_{i,t-1}) \\
	& \;+\; \beta_{5}(Number \; of \; Conflicts_{i,t-1}) \;+\; \beta_{6}(Upper \; Income_{i,t}) \\	
	& \;+\; \beta_{7}(Inflation_{i,t-1}) \;+\; \beta_{8}(Democracy_{i,t-1}) \\
	& \;+\; \beta_{9}(Resource \; Rents/GDP_{t-1}) \;+\; \beta_{10}(World \; GDP \; Growth_{t})
\end{align*}

\subsection{Baseline Model}

Before we move to discussing the results of the model specification that we have described above we estimate a simple, baseline model to assess the effect of any civil conflict on growth. For this model we use a specification as similar as possible to the one we explicated in the previous section, with the key difference being that this baseline model is estimated using a full country-year panel with fixed effects.\footnote{In choosing between fixed and random effects, we again followed the typology set out by \citet{clark:linzer:2015}, and, in this case, found that the fixed effects specification was preferred.} The dependent variable is again annual percent change in GDP from the World Development Indicators, and the key independent variable here is whether or not the country was engaged in a civil war in the previous year according to the PRIO Conflict dataset. Since we are using a full country-year panel, we have to omit the PRIO conflict specific variables (e.g., conflict intensity, conflict duration) as they are undefined for country-year observations in which no conflict was taking place. The rest of the independent variables are similar to the model specified in the previous section, the exact estimation model we use is shown below:

\begin{align*}
	\% \Delta GDP_{i,t} &= \beta_{1}(Civil War)_{i,t-1}) \\
	& beta_{6}(Upper \; Income_{i,t}) \;+\; \beta_{7}(Inflation_{i,t-1}) \\	
	& \beta_{8}(Democracy_{i,t-1}) \;+\; \beta_{9}(Resource \; Rents/GDP_{t-1}) \\
	& \;+\; \beta_{10}(World \; GDP \; Growth_{t})
\end{align*}

The results of this model are shown below in figure~\ref{fig:civWarCoefplot}. We will eschew discussing the controls since the primary purpose of this analysis is to determine a baseline effect for civil war.

\begin{figure}
	\resizebox{.45\textwidth}{!}{\input{civWarCoefPlot.tex}}
	\caption{Fixed effects regression results using full country-year panel. Darker colors indicates that the coefficient estimate is significantly different from zero at a 95\% CI, while lighter the same for a 90\% CI. Grey indicates that the estimate is not significantly different from zero at either of those intervals.}
	\label{fig:civWarCoefplot}
\end{figure}

@@
